---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    toc: yes
  pdf_document:
    toc: yes
---

## Load Libraries
```{r setup}
#knitr::opts_chunk$set(include = FALSE)
library(tidyverse)
library(ggplot2)
library(knitr)
```

## Different coding language
In the R notebook different coding languages can be used such as bash
```{bash}
ls
```
## Demo Data
Use built in R datasets, esoph. Data from a case-control study of esophageal cancer in Ille-et-Vilaine, France
Is a data frame with records of 88 indvidals with their alcohol and tobacco status, and how many cases of noncases in each combination catorgey
```{r summary(esoph), echo=TRUE}
summary(esoph)
```
## Demo Question
Which age group has the highest number of alcohol consumption that are cases?

### Base R code example 
```{r echo=TRUE, message=FALSE, warning=FALSE}
case_df1a <- esoph[c("agegp","alcgp","ncases")]  #select variables 
case_df1b <- case_df1a[order(case_df1a$ncases, decreasing = TRUE),] #reorder in decreasing
kable(head(case_df1b))
```

### Tidyverse R code example 
```{r echo=TRUE}
case_df2 <- esoph  %>% select(c(agegp,alcgp,ncases)) %>% arrange(desc(ncases)) 
kable(head(case_df2))
```

## Demo Plot
Tidyverse plot the number of cases in each Alcohol Consumption group by ages 
```{r esoph, echo=TRUE}
ggplot(case_df2,aes(x=alcgp, y=ncases, fill=agegp)) +
        geom_bar(position="dodge", stat="identity") +
        xlab("Alcohol Consumption") + ylab("Number of Cases") +
        labs(fill = "Age Group")
```

